### 2022-04-08 manuscript.tex
hmm [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/e0977775368cdf68ea6d2822abaadc5364aa0e6b.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/e0977775368cdf68ea6d2822abaadc5364aa0e6b/checks
https://github.com/scherzerthesis/thesis/actions/runs/2116570822

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/afca29ccc7e85bd9ed22a802be561104666cc46a/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/afca29ccc7e85bd9ed22a802be561104666cc46a}{scherzerthesis/thesis@afca29c}
on April 8, 2022.

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/e0977775368cdf68ea6d2822abaadc5364aa0e6b/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/e0977775368cdf68ea6d2822abaadc5364aa0e6b}{scherzerthesis/thesis@e097777}
on April 8, 2022.
